Assignment 2

### 2019-08-08 ex2/report/report.tex
Fix learn.py and delete plots in report

@@

\begin{figure*}[p]
\includegraphics[width=0.48\textwidth]{plots/pdp/sourceTransportPort_nn.pdf}
\includegraphics[width=0.48\textwidth]{plots/pdp/sourceTransportPort_rf.pdf}

\includegraphics[width=0.48\textwidth]{plots/pdp/apply(mean(ipTTL),forward)_nn.pdf}
\includegraphics[width=0.48\textwidth]{plots/pdp/apply(mean(ipTTL),forward)_rf.pdf}

\includegraphics[width=0.48\textwidth]{plots/pdp/apply(stdev(ipTotalLength),forward)_nn.pdf}
\includegraphics[width=0.48\textwidth]{plots/pdp/apply(stdev(ipTotalLength),forward)_rf.pdf}

@@

\begin{figure*}[p]
\includegraphics[width=0.48\textwidth]{plots/ale/sourceTransportPort_nn.pdf}
\includegraphics[width=0.48\textwidth]{plots/ale/sourceTransportPort_rf.pdf}

\includegraphics[width=0.48\textwidth]{plots/ale/apply(mean(ipTTL),forward)_nn.pdf}
\includegraphics[width=0.48\textwidth]{plots/ale/apply(mean(ipTTL),forward)_rf.pdf}

\includegraphics[width=0.48\textwidth]{plots/ale/apply(stdev(ipTotalLength),forward)_nn.pdf}
\includegraphics[width=0.48\textwidth]{plots/ale/apply(stdev(ipTotalLength),forward)_rf.pdf}

@@

\begin{figure*}[p]
\includegraphics[width=0.48\textwidth]{plots/ice/sourceTransportPort_nn_0.pdf}
\includegraphics[width=0.48\textwidth]{plots/ice/sourceTransportPort_rf_0.pdf}

\includegraphics[width=0.48\textwidth]{plots/ice/apply(mean(ipTTL),forward)_nn_0.pdf}
\includegraphics[width=0.48\textwidth]{plots/ice/apply(mean(ipTTL),forward)_rf_0.pdf}

\includegraphics[width=0.48\textwidth]{plots/ice/apply(stdev(ipTotalLength),forward)_nn_0.pdf}
\includegraphics[width=0.48\textwidth]{plots/ice/apply(stdev(ipTotalLength),forward)_rf_0.pdf}

@@

\begin{figure*}[p]
%\includegraphics[width=0.48\textwidth]{plots/pdp/sourceTransportPort_nn_bd.pdf}
%\includegraphics[width=0.48\textwidth]{plots/pdp/sourceTransportPort_rf_bd.pdf}

\includegraphics[width=0.48\textwidth]{plots/pdp/apply(stdev(ipTTL),forward)_nn.pdf}
\includegraphics[width=0.48\textwidth]{plots/pdp/apply(stdev(ipTTL),forward)_rf.pdf}

\includegraphics[width=0.48\textwidth]{plots/pdp/apply(stdev(ipTTL),forward)_nn_bd.pdf}
\includegraphics[width=0.48\textwidth]{plots/pdp/apply(stdev(ipTTL),forward)_rf_bd.pdf}

%\includegraphics[width=0.48\textwidth]{plots/pdp/apply(stdev(ipTotalLength),forward)_nn_bd.pdf}
%\includegraphics[width=0.48\textwidth]{plots/pdp/apply(stdev(ipTotalLength),forward)_rf_bd.pdf}

>>>>

\todo{We should only add the backdoor in forward direction actually. But it doesn't really matter I guess.}

@@

\begin{figure*}[p]
\includegraphics[width=0.48\textwidth]{../pdp/sourceTransportPort_nn.pdf}
\includegraphics[width=0.48\textwidth]{../pdp/sourceTransportPort_rf.pdf}

\includegraphics[width=0.48\textwidth]{../pdp/apply(mean(ipTTL),forward)_nn.pdf}
\includegraphics[width=0.48\textwidth]{../pdp/apply(mean(ipTTL),forward)_rf.pdf}

\includegraphics[width=0.48\textwidth]{../pdp/apply(stdev(ipTotalLength),forward)_nn.pdf}
\includegraphics[width=0.48\textwidth]{../pdp/apply(stdev(ipTotalLength),forward)_rf.pdf}

@@

\begin{figure*}[p]
\includegraphics[width=0.48\textwidth]{../ale/sourceTransportPort_nn.pdf}
\includegraphics[width=0.48\textwidth]{../ale/sourceTransportPort_rf.pdf}

\includegraphics[width=0.48\textwidth]{../ale/apply(mean(ipTTL),forward)_nn.pdf}
\includegraphics[width=0.48\textwidth]{../ale/apply(mean(ipTTL),forward)_rf.pdf}

\includegraphics[width=0.48\textwidth]{../ale/apply(stdev(ipTotalLength),forward)_nn.pdf}
\includegraphics[width=0.48\textwidth]{../ale/apply(stdev(ipTotalLength),forward)_rf.pdf}

@@

\begin{figure*}[p]
\includegraphics[width=0.48\textwidth]{../ice/sourceTransportPort_nn_0.pdf}
\includegraphics[width=0.48\textwidth]{../ice/sourceTransportPort_rf_0.pdf}

\includegraphics[width=0.48\textwidth]{../ice/apply(mean(ipTTL),forward)_nn_0.pdf}
\includegraphics[width=0.48\textwidth]{../ice/apply(mean(ipTTL),forward)_rf_0.pdf}

\includegraphics[width=0.48\textwidth]{../ice/apply(stdev(ipTotalLength),forward)_nn_0.pdf}
\includegraphics[width=0.48\textwidth]{../ice/apply(stdev(ipTotalLength),forward)_rf_0.pdf}

@@

\begin{figure*}[p]
%\includegraphics[width=0.48\textwidth]{../pdp/sourceTransportPort_nn_bd.pdf}
%\includegraphics[width=0.48\textwidth]{../pdp/sourceTransportPort_rf_bd.pdf}

\includegraphics[width=0.48\textwidth]{../pdp/apply(stdev(ipTTL),forward)_nn.pdf}
\includegraphics[width=0.48\textwidth]{../pdp/apply(stdev(ipTTL),forward)_rf.pdf}

\includegraphics[width=0.48\textwidth]{../pdp/apply(stdev(ipTTL),forward)_nn_bd.pdf}
\includegraphics[width=0.48\textwidth]{../pdp/apply(stdev(ipTTL),forward)_rf_bd.pdf}

%\includegraphics[width=0.48\textwidth]{../pdp/apply(stdev(ipTotalLength),forward)_nn_bd.pdf}
%\includegraphics[width=0.48\textwidth]{../pdp/apply(stdev(ipTotalLength),forward)_rf_bd.pdf}
